Z-Resonance at LEP

### 2010-07-27 Z0-Publikation/tex/paper-template.tex
add tables
selection besser

To be able to separate muonic events from background it is suitable to ask for
an angle of almost π, as the $Z^0$ boson should be created almost resting in
the laboratory frame, leading to muons flying back to back. Another selection
for muonic events is possible through the requirement of one muon carrying
about half the energy of the event and the other muon carrying a little less
energy than the first muon, but still more than \SI{40}{\percent} of the event
energy.

@@

>>>>

To be able to separate muonic events from background it is suitable to ask for
an angle of almost π, as the $Z^0$ boson should be created almost resting in
the laboratory frame, leading to muons flying back to back. Another selection
for muonic events is possible through the requirement of both muons carrying
about half the energy of the event each. This is possible because muon energies
can be measured very well.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
energy $\sqrt{s}$ [\si{\GeV}] & hadronic events & cross section $σ_0^μ$ [\si{\nano\barn}]\\
\hline
89.48 & 1848 ± 43 ± 52 & 10.55 ± 0.18 ± 0.16 \\
91.33 & 3980 ± 63 ± 79 & 29.98 ± 0.49 ± 0.43 \\
93.02 & 2149 ± 46 ± 51 & 14.56 ± 0.24 ± 0.24 \\
\hline
\end{tabular}
\vspace*{0.3cm}
\caption{\baselineskip=0.38cm analyzed hadronic events at different center of mass energies}
\label{tab:hadr_events}
\end{center}
\vspace*{-0.5cm}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
energy $\sqrt{s}$ [\si{\GeV}] & myon events & cross section $σ_0^μ$ [\si{\nano\barn}]\\
\hline
89.48 & \phantom{0}67 ± \phantom{0}8 ± \phantom{0}8  & 0.64 ± 0.03 ± 0.3 \\
91.33 & 122 ± 11 ± 10 & 1.53 ± 0.05 ± 0.4 \\
93.02 & \phantom{0}77 ± \phantom{0}9 ± \phantom{0}9 & 0.87 ± 0.04 ± 0.03 \\
\hline
\end{tabular}
\vspace*{0.3cm}
\caption{\baselineskip=0.38cm analyzed hadronic events at different center of mass energies}
\label{tab:myon_events}
\end{center}
\vspace*{-0.5cm}
\end{table}
